A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-04-24 notes/notes.tex
--no-message

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\vec k}\) is a normalisation factor and is defined by \(|\lambda_{\vec k}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice. Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.

It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
\begin{equation}\begin{aligned}
	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
\end{aligned}\end{equation}
In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\). Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.

The wavefunction can be even brought into the familiar Bloch function form:
\begin{equation}\begin{aligned}
	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\vec k} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
\end{aligned}\end{equation}
where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function. This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).

It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
\end{aligned}\end{equation}
At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
	&= \frac{1}{|\lambda_{\vec k}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
\end{aligned}\end{equation}
At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\). The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\vec k}\):
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\vec k}|^2 = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\vec k}|^2 = \delta_{\vec k, \vec k^\prime}
\end{aligned}\end{equation}
This concludes the proof of orthonormality.

@@

	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}

@@

	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \frac{N}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\vec k}|^2}\\

@@

In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\lambda_0 w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.

@@

	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_0|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}

@@

	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}

@@

	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}

@@

	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\

>>>>

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice. Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.

It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
\begin{equation}\begin{aligned}
	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
\end{aligned}\end{equation}
In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\). Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.

The wavefunction can be even brought into the familiar Bloch function form:
\begin{equation}\begin{aligned}
	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
\end{aligned}\end{equation}
where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function. This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).

It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
\end{aligned}\end{equation}
At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
\end{aligned}\end{equation}
At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\). The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
\end{aligned}\end{equation}
This concludes the proof of orthonormality.

@@

	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}

@@

	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\

@@

In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=\vec k_0}} = \frac{1}{\lambda_{\ket{\vec k_0}} w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian. Note that \(\vec k_0\) is simply the Bloch momentum of the ground state.

@@

	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}

@@

	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}

@@

	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}

@@

	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
